### 2023-03-29 main/chapter_experiment.tex
add electron resolution

\paragraph{Muons.}
Since hard muons are not stopped inside \atlas, their reconstruction derives
from the curved tracks they leave in the inner detector and muon system as they
traverse \atlas's strong magnetic fields.
High tracking fidelity allows us to reliably reconstruct muons across most of
their expected momentum spectrum, with $\sigma(\pt) / \pt \lesssim 10\%$ up to
$\pt \approx 1\,\eV[T]$.
But resolution must degrade as these tracks' curvatures reduce at very high
energies, and Figure~\ref{fig:atlas_cutaway} illustrates this degradation.
The relative momentum resolution is approximately Gaussian in
$\sigma(\pt) / \pt$ for muons across this momentum range
(and therefore non-Gaussian in $\pt$ itself)~\cite{atlas1999design1}.

@@

\paragraph{Electrons.}

\paragraph{Jets.}

\paragraph{Missing transverse momentum.}
\TODO{}

>>>>

\paragraph{Muons.}
Since hard muons are not stopped inside \atlas, their reconstruction derives
from the curved tracks they leave in the inner detector and muon system as they
traverse \atlas's strong magnetic fields.
High tracking fidelity allows us to reliably reconstruct muons across most of
their expected momentum spectrum, with $\sigma(\pt) / \pt \lesssim 10\%$ up to
$\pt \approx 1\,\eV[T]$.
But resolution must degrade as these tracks' curvatures reduce at very high
energies, and Figure~\ref{fig:atlas_cutaway} illustrates this degradation.
The relative momentum resolution is approximately Gaussian in
$1 / \pt$ for muons across this momentum range
(and therefore non-Gaussian in $\pt$ itself)~\cite{atlas1999design1}.

@@

\paragraph{Electrons.}
Electrons are measured by both tracking in the inner detector and calorimetry
in the electromagnetic calorimeter.
These two measurements give two complementary inputs that aid in electron
reconstruction.
As for muons, the resolution from tracking scales with $1/\pt$, but the
calorimetry error is dominated by Poisson statistics with a number of charged
particles that scales in proportion to the electron energy $E$.
Combining these two factors with a constant baseline noise, one can therefore
model the relative electron resolution as
\begin{equation}
\label{eqn:experiment_electron_resolution}
\frac{\sigma(E)}{E}
\approx
\frac{a_1}{\sqrt{E}}
\oplus
\frac{a_2}{\pt}
\oplus
a_3
\end{equation}
in which $\oplus$ indicates a sum in quadrature.
In \atlas, these $a_i$ parameters are roughly
$a_1 \approx 0.1\,\sqrt{\eV[G]}$,
$a_2 \approx 0.25\,\eV[G]$, and
$a_3 \approx 0.007$~\cite{nackenhorst2010top, Lester:705139, ERDMANN201418}.
Although resolutions vary across the solid angle, this formula roughly
reproduces the reported resolutions of
$\frac{\sigma(E)}{E} \approx 4\%$ at $E = \pt = 10\,\eV[G]$,
$\frac{\sigma(E)}{E} \approx 1\%$ at $E = \pt = 100\,\eV[G]$, and
$\frac{\sigma(E)}{E} \approx 0.1\%$ at
$E = \pt = 1\,\eV[T]$ for electrons~\cite{atlas2019electron}.

Energy losses from high-energy electrons are dominated by Bremsstrahlung
radiations, in which the electron radiates a photon and recoils from its
momentum.
Electron reconstruction algorithms efficiently recover this lost Bremsstrahlung
momentum by associating nearby photon calorimeter clusters back to their source
electron many cases~\cite{atlas1994proposal, atlas1999design1}.

\paragraph{Jets.}
\begin{equation}
\label{eqn:experiment_jet_resolution}
\frac{\sigma(E)}{E}
\approx
\frac{b_1}{\sqrt{E}}
\oplus
b_2
\end{equation}
with
$b_1 \approx 0.5\,\sqrt{\eV[G]}$ and
$b_2 \approx 0.03$.

\paragraph{Missing transverse momentum.}
\TODO{}
% Reference from Holly
%  ATLAS collaboration. ET
% miss performance in the ATLAS detector using 2015–2016 LHC
% pp collisions. ATLAS-CONF-2018-023, 2016.
